### 2022-03-18 paper/localpsf.tex
background section of paper is acceptable

Convolutions can be performed using the fast Fourier transform (FFT) \cite{PRODCONVFFT}, which allows PC approximations to be used as a fast surrogates for $\Aop$. Often it is necessary to perform further linear algebra operations involving $\Aop$, such as solving linear systems with $\Aop$ as the coefficient operator. Conventionally, one performs these linear algebra operations using Krylov methods, replacing $\Aop$ with its PC approximation \cite{PRODCONVKRYLOV}. The Krylov method is accelerated because performing matrix vector products with the product-convolution approximation is typically faster than performing operator actions with $\Aop$. However, there are several problems with this approach. First, the number of Krylov iterations can be large, particularly when $\Aop$ is high-rank. Second, complicated geometries are rarely discretized using regular grids, so using the FFT to perform convolutions requires transferring discretized functions back and forth between the irregular mesh and a regular grid. Third, the computational cost grows with the number of convolution kernels used. 
%If a large number of convolution kernels are used, this approach can be slow.
%Furthermore, in big-data inverse problems the required number of Krylov iterations is large \cite{MYDISSERTATION,OTHERS}. 
Thus, 
%after constructing the product-convolution approximation, 
it is desirable to convert the PC approximation to other matrix formats that are amenable to faster linear algebra operations. Wavelet compression methods have been used for this purpose \cite{PRODCONVWAVELETS}, because operators that are amenable to PC approximation are often sparse in the wavelet domain. Convolution-product approximations (transposes of PC approximations) are equivalent to low rank approximation of the pseudo-differential symbol of the operator, so one could perform linear algebra operations involving PC approximations using fast methods for pseudo-differential operator symbol calculus \cite{YINGDEMANET}. Here, we follow our previous work \cite{PRODCONVMYPAPER}, in which we converted PC approximations into H-matrix format.

@@

After discretization with finite elements\footnote{While we use finite elements, other discretization schemes such as finite differences or finite volumes could be used instead, with minor modifications to our method.} (Section \ref{sec:finite_element_kernel}), $\Aop$ and $\Phi$ become matrices $\mathbf{A}$ and $\mathbf{\Phi}$, respectively. Because $\Aop$ is only available matrix-free and $\Phi$ is only defined implicitly in terms of $\Aop$, the matrices $\mathbf{A}$ and $\mathbf{\Phi}$ are not easily accessible. Directly computing and storing these matrices is computationally intractible. In this section, we present our method for constructing accessible H-matrix approximations, $\mathbf{A}_H$ and $\mathbf{\Phi}_H$ of $\mathbf{A}$ and $\mathbf{\Phi}$, respectively, using a small number of operator actions of $\Aop$ and $\Aop^T$.

>>>>

Convolutions can be performed using the fast Fourier transform (FFT) \cite{PRODCONVFFT}, which allows PC approximations to be used as a fast surrogates for $\Aop$. Often it is necessary to perform further linear algebra operations involving $\Aop$, such as solving linear systems with $\Aop$ as the coefficient operator. Conventionally, one performs these linear algebra operations using Krylov methods, replacing $\Aop$ with its PC approximation \cite{PRODCONVKRYLOV}. The Krylov method is accelerated because performing matrix vector products with the product-convolution approximation is typically faster than performing operator actions with $\Aop$. However, there are several problems with this approach. First, the number of Krylov iterations can be large, particularly when $\Aop$ is high-rank. Second, complicated geometries are rarely discretized using regular grids, so using the FFT to perform convolutions requires transferring discretized functions back and forth between the irregular mesh and a regular grid. Third, the computational cost grows with the number of convolution kernels used. 
%If a large number of convolution kernels are used, this approach can be slow.
%Furthermore, in big-data inverse problems the required number of Krylov iterations is large \cite{MYDISSERTATION,OTHERS}. 
Thus, 
%after constructing the product-convolution approximation, 
it is desirable to convert the PC approximation to other matrix formats that are amenable to faster linear algebra operations. Wavelet compression methods have been used for this purpose \cite{PRODCONVWAVELETS}, because operators that are amenable to PC approximation are often sparse in the wavelet domain. Convolution-product approximations (transposes of PC approximations) are equivalent to low rank approximation of the pseudo-differential symbol of the operator, so one could perform linear algebra operations involving PC approximations using fast methods for pseudo-differential operator symbol calculus \cite{YINGDEMANET}. There are also other matrix-free operator approximation methods based on wavelets \cite{HERRMANN}, and pseudo-differential operators \cite{DEMANET}, that do not use PC approximation. Here, we follow our previous work \cite{PRODCONVMYPAPER}, in which we converted PC approximations into H-matrix format.

@@

After discretization with finite elements\footnote{While we use finite elements, other discretization schemes such as finite differences or finite volumes could be used instead, with minor modifications to our method.} (Section \ref{sec:finite_element_kernel}), $\Aop$ and $\Phi$ become large dense matrices $\mathbf{A}$ and $\mathbf{\Phi}$, respectively. Because $\Aop$ is only available matrix-free and $\Phi$ is only defined implicitly in terms of $\Aop$, the matrices $\mathbf{A}$ and $\mathbf{\Phi}$ are not easily accessible. Directly computing and storing these matrices is computationally intractible. In this section, we present our method for constructing accessible H-matrix approximations, $\mathbf{A}_H$ and $\mathbf{\Phi}_H$ of $\mathbf{A}$ and $\mathbf{\Phi}$, respectively, using a small number of operator actions of $\Aop$ and $\Aop^T$.
